Query Optimization for Dynamic Imputation

### 2017-05-10 paper/relatedwork.tex
paper: endless orphans
paper: add some discussion of trummer & koch paper

>>>>

The planning algorithm that we present has similarities to the multi-objective query optimizer in~\cite{trummer2014}.
Both algorithms handle plans which have multiple cost functions by maintaining sets of Pareto optimal plans and pruning plans which become dominated.
In \ProjectName{}, costs are expected to grow monotonically as the size of the plan increases, which simplifies the optimization problem significantly.
\cite{trummer2014} handles the more complex case of cost functions which are piecewise linear, but not necessarily monotonic.
